Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-10 src/tex/ms.tex
[showyourwork] overleaf sync

In the non-eccentric case (i.e., with a circular orbit and where the coronagraphic mask centred on the star), minimum ($\varphi_\mathrm{min}$) and maximum ($\varphi_\mathrm{max}$) scattering phase angles accessible are symmetric about 90 degrees. 
%
We define the angle $\Delta \phi$ such that: 
\begin{equation}
    \label{eq:Delta_phi}
    \Delta \phi 
    = \phi_\mathrm{max} - \phi_\mathrm{min}
    =  2(\phi_\mathrm{max} - 90) 
    =  2(\phi_\mathrm{min} + 90)
\end{equation}

The on-sky projected planet distance, $r_\mathrm{proj}$ (in \si{\au}) is shown in \cref{fig:scattering-angle} assuming a non-eccentric circular orbit with a semi-major $a$ (in \si{\au}) at a distance $d_*$ (in \si{\parsec}) from the observer. 
%
The scattering phase angle $\phi$ is this set up follows the equation,
\begin{equation}
    \sin(\phi) = \frac{r_\mathrm{proj}}{a}
\end{equation}
%
Using small angles, $r_\mathrm{proj} = \delta d_*$ where $\delta$ is the angular separation on-sky.
%
We access the minimum scattering angle when the projected distance reaches the inner working angle separation $\delta = \mathrm{IWA}$. 
%
Using \cref{eq:Delta_phi}, we deduce:

@@

The Habitable Worlds Observatory is a coronagraphic space mission envisioned to detect and characterise Earth-like exoplanets in the 2040s \todo{check}. 
%
The instrument design and capabilities are still under development and thus can be driven by the science goals of the mission.
%
In this work, we investigated the possibility of using \hwo\ to detect different scattering phenomena which can be used to indicate the habitability of an exoplanet. \todo{more of why this is cool}

>>>>

In the non-eccentric case (i.e., with a circular orbit and where the coronagraphic mask centred on the star), minimum ($\varphi_\mathrm{min}$) and maximum ($\varphi_\mathrm{max}$) scattering phase angles accessible are symmetric about 90 degrees. 
%
We define the angle $\Delta \varphi$ such that: 
\begin{equation}
    \label{eq:Delta_phi}
    \Delta \varphi 
    = \varphi_\mathrm{max} - \varphi_\mathrm{min}
    =  2(\varphi_\mathrm{max} - 90) 
    =  2(\varphi_\mathrm{min} + 90)
\end{equation}

The on-sky projected planet distance, $r_\mathrm{proj}$ (in \si{\au}) is shown in \cref{fig:scattering-angle} assuming a non-eccentric circular orbit with a semi-major $a$ (in \si{\au}) at a distance $d_*$ (in \si{\parsec}) from the observer. 
%
The scattering phase angle $\phi$ is this set up follows the equation,
\begin{equation}
    \sin(\varphi) = \frac{r_\mathrm{proj}}{a}
\end{equation}
%
Using small angles, $r_\mathrm{proj} = \delta d_*$ where $\delta$ is the angular separation on-sky.
%
We access the minimum scattering angle when the projected distance reaches the inner working angle separation $\delta = \mathrm{IWA}$. 
%
Using \cref{eq:Delta_phi}, we deduce:

@@

The Habitable Worlds Observatory is a coronagraphic space mission envisioned to detect and characterise Earth-like exoplanets in the 2040's \todo{check}. 
%
The instrument design and capabilities are still under development and thus can be driven by the science goals of the mission.
%
In this work, we investigated the possibility of using \hwo\ to detect different scattering phenomena which can be used to indicate the habitability of an exoplanet. \todo{more of why this is cool}
